\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-16 challenges.tex
several minor

@@

One challenge particular to the context of 15-410 is that the kernels Landslide must be able to test may all use slightly different implementations to achieve the same goals. For Landslide to be generally applicable to (almost) any kernel that students may submit, it must make some abstract assumptions about the kernel design which are compatible with many different implementations.

>>>>

\revision{In this chapter, we discuss several problems that stand in the way of systematic exploration's applicability to kernel space. We address these problems in part with certain aspects of Landslide's design and in part by relying on the user to provide important information, which we discuss in Chapter~\ref{sec:design} and Chapter~\ref{sec:using} respectively.}

@@

One challenge particular to the context of 15-410 is that the kernels Landslide must be able to test may all use slightly different implementations to achieve the same goals.
\revision{While 15-410's kernel project mandates that students implement the Pebbles specification, students are free to make their own design decisions under the hood, which can result in significantly different scheduler behaviour among multiple kernels. In general, Landslide may rely on concrete details provided by kernel specifications, but must be compatible with arbitrary implementation details.}
For Landslide to be generally applicable to many different kernels, even only multiple ones that implement the same specification (such as Pebbles), it must make some abstract assumptions about the kernel design which are compatible with many different implementations.

### 2012-05-16 evaluation.tex
several minor

While building Landslide, we worked primarily with two kernels: one, the kernel the author wrote as a student in 15-410 (Fall 2008), and another, a kernel the author graded as a TA for 15-410 (Fall 2011). With permission, we refer to the first kernel as ``POBBLES'' and the second as ``LudicrOS''.

@@

In short, even though Landslide may give false negatives from using imperfect sets of decision points, the exploration itself must be sound (i.e. not missing any bugs that exist in the resulting tree).\footnote{
When running LudicrOS yield/vanish with decision points on \texttt{mutex\_unlock} but not on \texttt{mutex\_lock}, we found that the ordering invariant failed: ``backwards'' exploration found no bug, while ``forwards'' exploration did. We attribute this to a bug in Landslide itself, and present the results for the backwards exploration as usual, in which Landslide found no bug.}

>>>>

While building Landslide, we worked primarily with two kernels: one, the kernel the author wrote as a student in 15-410 (Fall 2008), and another, a kernel the author graded as a TA for 15-410 (Fall 2011). We refer to the first kernel as ``POBBLES'' and to the second, with permission, as ``LudicrOS''.

@@

In short, even though Landslide may give false negatives from using imperfect sets of decision points, the exploration itself must be sound (i.e. not missing any bugs that exist in the resulting tree).

When running LudicrOS yield/vanish with decision points on \texttt{mutex\_unlock} but not on \texttt{mutex\_lock}, we found that the ordering invariant failed: ``backwards'' exploration found no bug, while ``forwards'' exploration did. We attribute this to a bug in Landslide itself, and present the results for the backwards exploration as usual, in which Landslide found no bug.
